---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# broadcastPower

<!-- badges: start -->
Compute broadcast power and compare with FCC data. 
[![R-CMD-check](https://github.com/sbgraves237/broadcastPower/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/sbgraves237/broadcastPower/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The simplest part of this package is the function `FCCquery`.  That creates a character
string that begins `https://transition.fcc.gov/fcc-bin/` and the uses [`xml2::read_html`](https://xml2.r-lib.org/reference/read_xml.html) to extract information on all the broadcasters with `dist km` of a (lat, lon) location.  

More sophisticated parts of this package will process fast fourier transforms of signal strenth for each broadcaster measured by appropriate test equipment.  

## Installation

You can install the development version of broadcastPower from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sbgraves237/broadcastPower")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(broadcastPower)
(FCCstr1 <- FCCqueryString())
```

This returns all the broadcasters within 80 km of FCC headquarters in Washington, DC.  The function `FCCquery` will then pass that to `xml2::read_html` to download the desired information and parse it into a `data.frame`. 

